\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-11 paper/ms.tex
Likelihood and print

>>>>

The log-likelihood code is:
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::log_likelihood() const
{
    // Grab the dataset
    const std::vector<double>& x = Data::get_instance().get_x();
    const std::vector<double>& y = Data::get_instance().get_y();

    // Variance
    double var = sigma*sigma;

    // Conventional gaussian sampling distribution
    double log_L = 0.0;
    double mu;
    for(size_t i=0; i<y.size(); ++i)
    {
        mu = m*x[i] + b;
        log_L += -0.5*log(2*M_PI*var) - 0.5*pow(y[i] - mu, 2)/var;
    }

    return log_L;
}
\end{CodeInput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeInput}
void StraightLine::print(std::ostream& out) const
{
    out<<m<<' '<<b<<' '<<sigma;
}

std::string StraightLine::description() const
{
    return std::string("m, b, sigma");
}

\end{CodeInput}
\end{CodeChunk}
